Internet of Things: a Real-World Deployment Towards Smart Grids Integration

### 2013-07-08 doc/thesis/report.tex
Things is in italic and typos fixed

\chapter{Abstract}
\paragraph{}
Information Technology is advancing exponentially and largely impacting our daily lives. The current evolution in computing is the \gls{iot}. It is smoothly evolving from an Internet of people to and Internet of Things. By 2020, it is expected to have 50 billion "Things" connected to the Internet. 
\paragraph{}
However such a migration induces a strong level of complexity when handling interoperability between heterogeneous Things, i.g. Wireless Sensors, RFID, and mobile devices.
\paragraph{}
In this thesis, we focus on the  integration of wireless sensors into \gls{iot}. This is q prologue for the future integration of \gls{sg} into \gls{iot}. In this work, we deployed a smart building testbed for energy optimization, and for integration into \gls{sg}\glsreset{sg}.
\paragraph{}
The testbed built provides IPv6 gatewaying, remote control of wireless sensor nodes which is built on top of \gls{6lowpan}\glsreset{6lowpan}, and mobile access to the system.
\paragraph{}
The system is using different technologies such as \gls{tinyos}, \gls{nesc}, \gls{j2se} and  \gls{http}.

@@

\section{General Architecture of the System}
\paragraph{}
The general architecture is depicted in figure \ref{fig:gen_architecture}. This figure shows the existing components and their interactions. Each set of components appear within a box as this last refers to what hardware are the components deployed in as it is labeled in the box.
\begin{figure}[htbp]
\centering
\includegraphics[width=17cm,height=17cm,keepaspectratio]{img/general_architecture.jpg}
\caption{General architecture depicting the main components of the system}
\label{fig:gen_architecture}
\end{figure}
%\clearpage
\paragraph{}
Now that the general architecture has been defined, the question that should be asked is whether all these components operate in the same layer in the \gls{osi} model and if not, in which layer does each of these components reside. As an answer to such a question, figure \ref{fig:layered_view} is here to show on what layer does every component act on.

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.40]{img/layered_view.jpg}
\caption{Layered view showing where every component appears in the \gls{osi} model}
\label{fig:layered_view}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.8]{img/ct.jpg}
\caption{Current transformer}
\label{fig:current_transformer}
\end{figure}

@@

\section{IPv6 over USB Tunnel}
\paragraph{}
This program is installed in the gateway server machine. The sink gets connected to the gateway using \gls{usb}, the gateway will recognize it as a network interface card that uses \gls{ipv6} as a network technology. Moreover, this component is part of the \gls{blip} software package which the network interface card module and starts extracting incoming \gls{ipv6} packets from the \gls{usb} frames and encapsulates outgoing \gls{ipv6} into \gls{usb} frames.
\paragraph{}
The installation and initialization of this component will be detailed in appendix A.
\section{\gls{ipv4}/\gls{ipv6} Gatewaying Process}
\paragraph{}
This component is in charge of hiding the heterogeneity of the system from the rest of the components of the system and also the outside world. It does so by intercepting all the packets and transforms the ones of interest to meet the standards used by the recipient.
\paragraph{}
To make use of this process, there is an initial configuration that should be performed on all the components of the system in order for the system to work (explained in Appendix A). The gateway has two network interface cards: the Wi-Fi interface and the Zigbee interface provided through the tunnel. The first one is using \gls{ipv4} whereas the second is using \gls{ipv6}.
\paragraph{}
The program has three subcomponents as seen in section 4.8. The three components are the following:
\begin{itemize}
\item Packet sniffer
\item Packet transformer
\item Address translator
\end{itemize}
The following subsections will discuss each of these subcomponent separately from the implementation point of view.

@@

\begin{table}[htbp]
    \begin{tabular}{ll}
    \hline
    Delay (ms) & Jitter (ms) \\ \hline
    0.1        & 0.0         \\ 
    \end{tabular}
    \caption{Experiment 2 delay and jitter}
        \label{table:exp2}
\end{table}
\paragraph{}
The transformation process's elapsed time is measured in milliseconds and from table \ref{table:exp2}, one can see that the average delay is on average 0.1 milliseconds whereas the jitter is around 0 milliseconds meaning that the process's time varies between a few nanoseconds to at most 150 nanoseconds. Depending on the machine's load.
\paragraph{}
 The Packet transformation process is a component that shows excellent results. Before conducting experiment 2, we were persuaded that there will be additional delay originating from this process and it could be responsible for the high delay seen in experiment 1. However, the results show otherwise and that the component is not to be put responsible for such an important delay seen in experiment 1.

>>>>

\chapter{Abstract}
\paragraph{}
Information Technology is growing exponentially and largely impacting our daily lives. The current evolution in computing is the \gls{iot}. It is smoothly evolving from an Internet of people to and Internet of \textit{Things}. By 2020, it is expected to have 50 billion \textit{Things} connected to the Internet. 
\paragraph{}
However, such a migration induces a strong level of complexity when handling interoperability between heterogeneous \textit{Things}, e.g. Wireless Sensors, RFID, and mobile devices.
\paragraph{}
In this thesis, we focus on the integration of wireless sensors into \gls{iot}. This is a prologue for the future integration of \gls{sg} into \gls{iot}. In this work, we deployed a smart building test-bed for energy optimization, and for integration into \gls{sg}\glsreset{sg}.
\paragraph{}
The test-bed built provides IPv6 gatewaying, remote control of wireless sensor nodes which is built on top of \gls{6lowpan}\glsreset{6lowpan}, and mobile access to the system.
\paragraph{}
The system is using different technologies such as \gls{tinyos}, \gls{nesc}, \gls{j2se} and  \gls{http}.

@@

\section{General Architecture of the System}
\paragraph{}
The general architecture is depicted in figure \ref{fig:gen_architecture}. This figure shows the existing components and their interactions. Each set of components appear within a box as this last refers to what hardware are the components deployed in as it is labeled in the box.
\begin{figure}[htbp]
\centering
\includegraphics[width=17cm,height=20cm,keepaspectratio]{img/general_architecture.jpg}
\caption{General architecture depicting the main components of the system}
\label{fig:gen_architecture}
\end{figure}
%\clearpage
\paragraph{}
Now that the general architecture has been defined, the question that should be asked is whether all these components operate in the same layer in the \gls{osi} model and if not, in which layer does each of these components reside. As an answer to such a question, figure \ref{fig:layered_view} is here to show in what layer does every component operates.

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.40]{img/layered_view.jpg}
\caption{Layered view showing where every component operates in the \gls{osi} model}
\label{fig:layered_view}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.7]{img/ct.jpg}
\caption{Current transformer}
\label{fig:current_transformer}
\end{figure}

@@

\section{IPv6 over USB Tunnel}
\paragraph{}
This program is installed in the gateway server machine. The sink gets connected to the gateway using \gls{usb}, the gateway will recognize it as a network interface card that uses \gls{ipv6} as a network technology. Moreover, this component is part of the \gls{blip} software package which the network interface card module and starts extracting incoming \gls{ipv6} packets from the \gls{usb} frames and encapsulates outgoing \gls{ipv6} into \gls{usb} frames.
\paragraph{}
The installation and initialization of this component will be detailed in appendix A.
\section{IPv4/IPv6 Gatewaying Process}
\paragraph{}
This component is in charge of hiding the heterogeneity of the system from the rest of the components of the system and also the outside world. It does so by intercepting all the packets and transforms the ones of interest to meet the standards used by the recipient.
\paragraph{}
To make use of this process, there is an initial configuration that should be performed on all the components of the system in order for the system to work (explained in Appendix A). The gateway has two network interface cards: the Wi-Fi interface and the Zigbee interface provided through the tunnel. The first one is using \gls{ipv4} whereas the second is using \gls{ipv6}.
\paragraph{}
The program has three subcomponents as seen in section 4.8. The three components are the following:
\begin{itemize}
\item Packet sniffer
\item Packet transformer
\item Address translator
\end{itemize}
The following subsections will discuss each of these subcomponent separately from the implementation point of view.

@@

\begin{table}[htbp]
    \begin{tabular}{ll}
    \hline
    Delay (ms) & Jitter (ms) \\ \hline
    0.1        & 0.0         \\ 
    \end{tabular}
    \caption{Experiment 2 delay and jitter}
        \label{table:exp2}
\end{table}
\paragraph{}
The transformation process's elapsed time is measured in milliseconds and from table \ref{table:exp2}, one can see that the average delay is on average 0.1 milliseconds whereas the jitter is around 0 milliseconds meaning that the process's time varies between a few nanoseconds to at most 150 nanoseconds. Depending on the machine's load. The distribution of the delay frequency is shown the histogram depicted in figure \ref{fig:histogram}. From this figure one can conclude that the delay is normally distributed
\begin{figure}[htbp]
 \centering
 \includegraphics[scale=0.9]{img/histogram.JPG}
 \caption{Delay frequency histogram}
 \label{fig:histogram}
 \end{figure}
\paragraph{}
 The Packet transformation process is a component that shows excellent results. Before conducting experiment 2, we were persuaded that there will be additional delay originating from this process and it could be responsible for the high delay seen in experiment 1. However, the results show otherwise and that the component is not to be put responsible for such an important delay seen in experiment 1.
